random forest and lme

### 2020-04-09 src/rf.Rmd

```{r}
suppressPackageStartupMessages(library(randomForest))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(nlme))
suppressPackageStartupMessages(library(ROCR))
```

@@

# Linear Mixed Effect Model
```{r}
# both random slope and random intercept
# different rate of change of assessment value and mill rate as well as initial assessment value and mill rate for each municipality 
lme.mill <- lme( mill.rate ~  tax.class + municipality + total.assessment + past.mill,na.action = na.omit, data=train, random = ~ 1 + total.assessment + past.mill | municipality, method = "ML")

@@

lme.as <- lme(next.assess ~  tax.class + municipality + total.assessment + mill.rate ,na.action = na.omit, data=train, random = ~ 1 + total.assessment + mill.rate | municipality, method = "ML")

@@

>>>>

```{r}
suppressPackageStartupMessages(library(randomForest))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(ROCR))
suppressPackageStartupMessages(library(predictmeans))
```

@@

# Linear Mixed Effect Model
```{r}
# both random slope and random intercept
# different rate of change of assessment value and mill rate as well as initial assessment value and mill rate for each municipality

lme.mill <- lmer(mill.rate ~ 1+ (1+year|municipality) + as.factor(year) + tax.class  + total.assessment + past.mill, data = train)

@@

lme.as <- lmer(next.assess ~ 1+ (1+year|municipality) + as.factor(year) + tax.class + total.assessment + mill.rate, data = train)

@@

```{r}
# check assumptions of lme

# Homogeneity of Variance
residplot(lme.mill)
residplot(lme.as)
```
